CRUSE to Safe Cycling in Ireland

### 2023-09-11 cruse-paper.qmd
PDF version

---
title: "CRUSE to Safe Cycling in Ireland"
subtitle: An Open Source Methodology to Support Active Travel
author:
  - name: Dr. Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Dr. Joey Talbot
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Eugeni Vidal Tortosa
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Hussein Mahfouz
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Dan Brennan
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Dr. Suzanne Meade
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Elaine Brick
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Peter Wright
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, EXETER, EX5 1FY, UK
abstract: |
  Under the EU Road infrastructure safety management (RISM) directive, the National Road Safety Strategy (RSS), and the Climate Action Plan Transport Infrastructure Ireland (TII) has a remit for road safety and decarbonizing a predominantly road-based network in Ireland.

@@

  As countries, like Ireland, invest in cycling, the number of killed and seriously injured cyclists must reduce too.
  The CRUSE Tool provides estimates of cycling potential and routing for each county in Ireland, and works in both urban and rural settings, to enable monitoring of cycling safety.
  With growth in the E-bike market, the tool will help inform inter-urban and rural networks to support the transfer of trips to sustainable modes for longer journeys.
  The CRUSE Tool methodology and findings are directly relevant to addressing the challenges and opportunities faced by other NRAs.
  The datasets resulting from the project are open access and can be used by both non-experts and professionals.
keywords: 
  - Cycling
  - Open-source
  - Road Safety
  - Active Travel
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
csl: apa.csl
---

## 10th Transport Research Arena, TRA 2024, Dublin, Ireland {.unnumbered}

@@

• Title page/main information (title, full names and institutional addresses for all
authors, indication of the corresponding author)
• Abstract
• Introduction
• Results
• Discussion (can be combined in ‘Results and Discussion’ section)
• Conclusions
• Methods/Experimental (can also be placed after Introduction)
• List of abbreviations
• Declarations*
o Availability of data and material
o Funding
o Acknowledgements
o Competing interests
o Authors' contributions
o Authors' information (optional)
o *If any of the sections are not relev

>>>>

---
title: "CRUSE to Safe Cycling in Ireland"
subtitle: An Open Source Methodology to Support Active Travel
bibliography: bibliography.bib
csl: apa.csl

# # Uncomment for draft versions:
# format: 
#   html:
#     output-file: index.html
#   pdf:
#     output-file: cruse-paper.pdf 
#   gfm:
#     output-file: README.md
# number-sections: true

# Uncomment the following line to produce the cover page
author:
  - name: Dr. Robin Lovelace
    email: r.lovelace@leeds.ac.uk
    corresponding: true
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Dr. Joey Talbot
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Eugeni Vidal Tortosa
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Hussein Mahfouz
    affiliations:
      - name: University of Leeds
        address: Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom
  - name: Dan Brennan
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Dr. Suzanne Meade
    affiliations:
      - name: Transport Infrastructure Ireland
        address: Parkgate Business Centre, Parkgate Street, Dublin 8, D08 DK10, Ireland
  - name: Elaine Brick
    affiliations:
      - name: AECOM
        address: Unit 6, Galway Technology Park, Parkmore, Galway, Ireland
  - name: Peter Wright
    affiliations:
      - name: AECOM
        address: Winslade House, Winslade Park, Manor Drive, Clyst St Mary, EXETER, EX5 1FY, UK
abstract: |
  Under the EU Road infrastructure safety management (RISM) directive, the National Road Safety Strategy (RSS), and the Climate Action Plan Transport Infrastructure Ireland (TII) has a remit for road safety and decarbonizing a predominantly road-based network in Ireland.

@@

  As countries, like Ireland, invest in cycling, the number of killed and seriously injured cyclists must reduce too.
  The CRUSE Tool provides estimates of cycling potential and routing for each county in Ireland, and works in both urban and rural settings, to enable monitoring of cycling safety.
  With growth in the E-bike market, the tool will help inform inter-urban and rural networks to support the transfer of trips to sustainable modes for longer journeys.
  The CRUSE Tool methodology and findings are directly relevant to addressing the challenges and opportunities faced by other NRAs.
  The datasets resulting from the project are open access and can be used by both non-experts and professionals.
keywords: 
  - Cycling
  - Open-source
  - Road Safety
  - Active Travel
date: last-modified
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
---

@@

• Title page/main information (title, full names and institutional addresses for all
authors, indication of the corresponding author)
• Abstract
• Introduction

# Methods

# Results

# Discussion

# Conclusions

# List of abbreviations

# Declarations

## Availability of data and material {.unnumbered}
## Funding {.unnumbered}
## Acknowledgements {.unnumbered}
## Competing interests {.unnumbered}
## Authors' contributions {.unnumbered}

# References {.unnumbered}
